### 2023-09-23 short/sections/selected-papers.tex
Update selected-papers.tex

\item{González-Bustamante, B., \& Aguilar, D. (2023). Territorial patterns of open e-government: evidence from Chilean municipalities. {\itshape Political Research Exchange, 5}(1), 2194369. {\scshape doi:} \href{https://doi.org/10.1080/2474736X.2023.2194369}{\textcolor{blue}{10.1080/2474736X.2023.2194369}}. {\scshape \footnotesize SocArXiv:} \href{https://doi.org/10.31235/osf.io/gt8a5}{\textcolor{blue}{10.31235/osf.io/gt8a5}}.}\vspace{1mm}

@@

\item{\small González-Bustamante, B. (2021). Evolution and early government responses to COVID-19 in South America. {\itshape World Development, 137}, 105180. {\scshape doi:} \href{https://doi.org/10.1016/j.worlddev.2020.105180}{\textcolor{blue}{10.1016/j.worlddev.2020.105180}}.}\vspace{1mm}

\item{\small González-Bustamante, B., Astete, M., \& Orvenes, B. (2020). Senior Public Managers: A Novel Dataset on Members of the Chilean Civil Service. {\itshape Revista de Gestión Pública, IX}(2), 151--169. {\footnotesize \scshape [in Spanish and English]}. {\scshape doi:} \href{https://doi.org/10.22370/rgp.2020.9.2.2920}{\textcolor{blue}{10.22370/rgp.2020.9.2.2920}}. {\scshape \footnotesize SocArXiv:} \href{https://doi.org/10.31235/osf.io/vshcz}{\textcolor{blue}{10.31235/osf.io/vshcz}}.}\vspace{1mm}

\item{\small González-Bustamante, B. (2020). The Politics-Administration Dichotomy: A Case Study of the Chilean Executive During the Democratic Post-Transition. {\itshape Bulletin of Latin American Research, 39}(5), 582--597. \\ {\scshape doi:} \href{https://doi.org/10.1111/blar.13044}{\textcolor{blue}{10.1111/blar.13044}}. {\scshape \footnotesize SocArXiv:} \href{https://doi.org/10.31235/osf.io/d52au}{\textcolor{blue}{10.31235/osf.io/d52au}}.}\vspace{1mm}

\item{\small González-Bustamante, B., Carvajal, A., \& González, A. (2020). Determinants of E-Government in the Municipalities: Evidence from the Chilean Case. {\itshape Gestión y Política Pública, XXIX}(1), 97--129. {\footnotesize \scshape [in Spanish]}. \\ {\scshape doi:} \href{http://dx.doi.org/10.29265/gypp.v29i1.658}{\textcolor{blue}{10.29265/gypp.v29i1.658}}. {\scshape \footnotesize SocArXiv:} \href{https://doi.org/10.31235/osf.io/fze3x}{\textcolor{blue}{10.31235/osf.io/fze3x}}.} \vspace{1mm}

\item{\small Maillet, A., González-Bustamante, B., \& Olivares, A. (2019). Public-Private Circulation and the Revolving Door in the Chilean Executive Branch (2000-2014). {\itshape Latin American Business Review, 20}(4), 367--387. \\ {\scshape doi:} \href{https://doi.org/10.1080/10978526.2019.1652099}{\textcolor{blue}{10.1080/10978526.2019.1652099}}.}\vspace{1mm}

\item{\small González-Bustamante, B. (2019). Gaps, Representation, and Elite-Mass Congruence in Chile and Uruguay. {\itshape Convergencia. Revista de Ciencias Sociales}, 80, 1--27. {\footnotesize \scshape [in Spanish]}. {\scshape doi:} \href{https://doi.org/10.29101/crcs.v26i80.11097}{\textcolor{blue}{10.29101/crcs.v26i80.11097}}. {\scshape \footnotesize SocArXiv:} \href{https://doi.org/10.31235/osf.io/cqym8}{\textcolor{blue}{10.31235/osf.io/cqym8}}.}\vspace{1mm} %% {\scshape url:}  \href{https://www.redalyc.org/jatsRepo/105/10559568002/index.html}{\textcolor{blue}{www.redalyc.org}}

\item{\small González-Bustamante, B. (2018). Civil Service Models in Latin America. In A. Farazmand (ed.), {\itshape Global Encyclopedia of Public Administration, Public Policy, and Governance}. Cham: Springer. {\scshape doi:} \href{https://doi.org/10.1007/978-3-319-20928-9\_2699}{\textcolor{blue}{10.1007/978-3-319-20928-9\_2699}}. {\scshape \footnotesize SocArXiv:} \href{https://doi.org/10.31235/osf.io/mp4qd}{\textcolor{blue}{10.31235/osf.io/mp4qd}}.}\vspace{1mm}

\item{\small González-Bustamante, B., \& Garrido-Vergara, L. (2018). Socialization, Trajectories and Post-Career of Ministers in Chile, 1990-2010. {\itshape Política y Gobierno, XXV}(1), 31--64. {\footnotesize \scshape [in Spanish]}. {\scshape url:} \href{http://www.politicaygobierno.cide.edu/index.php/pyg/article/view/1080}{\textcolor{blue}{www.politicaygobierno.cide.edu}}.}\vspace{1mm}

>>>>

\item{González-Bustamante, B., \& Aguilar, D. (2023). Territorial patterns of open e-government: evidence from Chilean municipalities. {\itshape Political Research Exchange, 5}(1). {\scshape doi:} \href{https://doi.org/10.1080/2474736X.2023.2194369}{\textcolor{blue}{10.1080/2474736X.2023.2194369}}. {\scshape \footnotesize SocArXiv:} \href{https://doi.org/10.31235/osf.io/gt8a5}{\textcolor{blue}{10.31235/osf.io/gt8a5}}.}\vspace{1mm}

@@

\item{González-Bustamante, B. (2021). Evolution and early government responses to COVID-19 in South America. {\itshape World Development, 137}, 105180. {\scshape doi:} \href{https://doi.org/10.1016/j.worlddev.2020.105180}{\textcolor{blue}{10.1016/j.worlddev.2020.105180}}.}\vspace{1mm}

%% \item{González-Bustamante, B., Astete, M., \& Orvenes, B. (2020). Senior Public Managers: A Novel Dataset on Members of the Chilean Civil Service. {\itshape Revista de Gestión Pública, IX}(2), 151--169. {\footnotesize \scshape [in Spanish and English]}. {\scshape doi:} \href{https://doi.org/10.22370/rgp.2020.9.2.2920}{\textcolor{blue}{10.22370/rgp.2020.9.2.2920}}. {\scshape \footnotesize SocArXiv:} \href{https://doi.org/10.31235/osf.io/vshcz}{\textcolor{blue}{10.31235/osf.io/vshcz}}.}\vspace{1mm}

\item{González-Bustamante, B., Astete, M., \& Orvenes, B. (2020). Altos directivos públicos: Un nuevo conjunto de datos de miembros del servicio civil chileno. {\itshape Revista de Gestión Pública, IX}(2), 151--169. {\scshape doi}: \\ \href{https://doi.org/10.22370/rgp.2020.9.2.2920}{\textcolor{blue}{10.22370/rgp.2020.9.2.2920}}. {\scshape \footnotesize SocArXiv:} \href{https://doi.org/10.31235/osf.io/vshcz}{\textcolor{blue}{10.31235/osf.io/vshcz}}.}\vspace{1mm}

\item{González-Bustamante, B. (2020). The Politics-Administration Dichotomy: A Case Study of the Chilean Executive During the Democratic Post-Transition. {\itshape Bulletin of Latin American Research, 39}(5), 582--597. \\ {\scshape doi:} \href{https://doi.org/10.1111/blar.13044}{\textcolor{blue}{10.1111/blar.13044}}. {\scshape \footnotesize SocArXiv:} \href{https://doi.org/10.31235/osf.io/d52au}{\textcolor{blue}{10.31235/osf.io/d52au}}.}\vspace{1mm}

%% \item{González-Bustamante, B., Carvajal, A., \& González, A. (2020). Determinants of E-Government in the Municipalities: Evidence from the Chilean Case. {\itshape Gestión y Política Pública, XXIX}(1), 97--129. {\footnotesize \scshape [in Spanish]}. \\ {\scshape doi:} \href{http://dx.doi.org/10.29265/gypp.v29i1.658}{\textcolor{blue}{10.29265/gypp.v29i1.658}}. {\scshape \footnotesize SocArXiv:} \href{https://doi.org/10.31235/osf.io/fze3x}{\textcolor{blue}{10.31235/osf.io/fze3x}}.} \vspace{1mm}

\item{González-Bustamante, B., Carvajal, A., \& González, A. (2020). Determinantes del gobierno electrónico en las municipalidades: Evidencia del caso chileno. {\itshape Gestión y Política Pública, XXIX}(1), 97--129. {\scshape doi:} \\ \href{http://dx.doi.org/10.29265/gypp.v29i1.658}{\textcolor{blue}{10.29265/gypp.v29i1.658}}. {\scshape \footnotesize SocArXiv:} \href{https://doi.org/10.31235/osf.io/fze3x}{\textcolor{blue}{10.31235/osf.io/fze3x}}.} \vspace{1mm}

\item{Maillet, A., González-Bustamante, B., \& Olivares, A. (2019). Public-Private Circulation and the Revolving Door in the Chilean Executive Branch (2000-2014). {\itshape Latin American Business Review, 20}(4), 367--387. \\ {\scshape doi:} \href{https://doi.org/10.1080/10978526.2019.1652099}{\textcolor{blue}{10.1080/10978526.2019.1652099}}.}\vspace{1mm}

%% \item{González-Bustamante, B. (2019). Gaps, Representation, and Elite-Mass Congruence in Chile and Uruguay. {\itshape Convergencia. Revista de Ciencias Sociales}, 80, 1--27. {\footnotesize \scshape [in Spanish]}. {\scshape doi:} \href{https://doi.org/10.29101/crcs.v26i80.11097}{\textcolor{blue}{10.29101/crcs.v26i80.11097}}. {\scshape \footnotesize SocArXiv:} \href{https://doi.org/10.31235/osf.io/cqym8}{\textcolor{blue}{10.31235/osf.io/cqym8}}.}\vspace{1mm} %% {\scshape url:}  \href{https://www.redalyc.org/jatsRepo/105/10559568002/index.html}{\textcolor{blue}{www.redalyc.org}}

\item{González-Bustamante, B. (2019). Brechas, representación y congruencia élite-ciudadanía en Chile y Uruguay. {\itshape Convergencia. Revista de Ciencias Sociales}, 80, 1--27. {\scshape doi}: \href{https://doi.org/10.29101/crcs.v26i80.11097}{\textcolor{blue}{10.29101/crcs.v26i80.11097}}. {\scshape \footnotesize SocArXiv:} \\ \href{https://doi.org/10.31235/osf.io/cqym8}{\textcolor{blue}{10.31235/osf.io/cqym8}}.}\vspace{1mm} %% {\scshape url:} \href{https://www.redalyc.org/jatsRepo/105/10559568002/index.html}{\textcolor{blue}{www.redalyc.org}}

\item{González-Bustamante, B. (2018). Civil Service Models in Latin America. In A. Farazmand (ed.), {\itshape Global Encyclopedia of Public Administration, Public Policy, and Governance}. Cham: Springer. {\scshape doi:} \href{https://doi.org/10.1007/978-3-319-20928-9\_2699}{\textcolor{blue}{10.1007/978-3-319-20928-9\_2699}}. {\scshape \footnotesize SocArXiv:} \href{https://doi.org/10.31235/osf.io/mp4qd}{\textcolor{blue}{10.31235/osf.io/mp4qd}}.}\vspace{1mm}

%% \item{González-Bustamante, B., \& Garrido-Vergara, L. (2018). Socialization, Trajectories and Post-Career of Ministers in Chile, 1990-2010. {\itshape Política y Gobierno, XXV}(1), 31--64. {\footnotesize \scshape [in Spanish]}. {\scshape url:} \href{http://www.politicaygobierno.cide.edu/index.php/pyg/article/view/1080}{\textcolor{blue}{www.politicaygobierno.cide.edu}}.}\vspace{1mm}

\item{González-Bustamante, B., \& Garrido-Vergara, L. (2018). Socialización, trayectorias y poscarrera de ministros en Chile, 1990-2010. {\itshape Política y Gobierno, XXV}(1), 31--64. {\scshape url:} \href{http://www.politicaygobierno.cide.edu/index.php/pyg/article/view/1080}{\textcolor{blue}{www.politicaygobierno.cide.edu}}.}\vspace{1mm}
